Rubin Observatory Scheduling Algorithm and Simulations

### 2023-01-05 ms.tex
Updates from Overleaf

\author[0000-0003-2874-6464]{Peter Yoachim}
\affiliation{Department of Astronomy, University of Washington, Seattle, WA, USA}

@@

\begin{figure}
    \epsscale{0.5}
    \plotone{plots/XMM_LSS10years.pdf}\\
    \plotone{plots/XMM_LSS_0.1.pdf}
    \plotone{plots/XMM_LSS_0.2.pdf}
    \caption{Examples of how DDF fields are pre-scheduled. The top plot shows the expected limiting depth for the XMM-LSS field (given nominal seeing conditions) over the course of the survey. The lower plots zoom in on two observing seasons, showing how observations would be scheduled using 90\% and 80\% of the potential season length respectively, with both using the constraint that scheduled observations reach depths deeper than 23.5 mag in $g$.}
    \label{fig:ddf_examples}
    \epsscale{1}
\end{figure}

@@

@@

>>>>

\author[0000-0003-2874-6464]{Peter Yoachim}
\affiliation{Department of Astronomy and the DiRAC Institute, University of Washington, Seattle, WA, USA}

@@

\begin{figure}
    \epsscale{0.5}
    \plotone{plots/XMM_LSS10years.pdf}
    \plotone{plots/XMM_LSScumulative.pdf}\\
    \plotone{plots/XMM_LSS_0.1.pdf}
    \plotone{plots/XMM_LSS_0.2.pdf}
    \caption{Examples of how DDF fields are pre-scheduled. The top plot shows the expected limiting depth for the XMM-LSS field (given nominal seeing conditions) over the course of the survey. The lower plots zoom in on two observing seasons, showing how observations would be scheduled using 90\% and 80\% of the potential season length respectively, with both using the constraint that scheduled observations reach depths deeper than 23.5 mag in $g$.}
    \label{fig:ddf_examples}
    \epsscale{1}
\end{figure}

@@

\citet{Awan2016} for discussion of dithering strategies.

@@

\begin{acknowledgments}
This work was facilitated through the use of advanced computational, storage, and networking infrastructure provided by the Hyak supercomputer system at the University of Washington
\end{acknowledgments}
